Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-09-08 ms.tex
added more stuff on Allan variance and updated plots of the GL dewar time series

\begin{figure*}
\gridline{\fig{raw_tser_crossDetectorS02Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S02 detector}
		\fig{raw_tser_crossDetectorS03Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S03 detector}}
\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.}\label{fig:GLtSeriesAcrossDetectors}
\end{figure*}

>>>>

\begin{figure*}
\gridline{\fig{raw_tser_crossDetectorS02Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S02 detector}
		\fig{raw_tser_crossDetectorS03Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S03 detector}}
		\fig{allan_var_removelinear_True_gl_across_detectors.pdf}{0.48\textwidth}{Allan variance diagram for the ratio of the S02 to S03 background-subtracted detector fluxes}
\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
\end{figure*}
